NFC and burnout in teachers - A replication and extension study

### 2021-08-26 Manuscript/Manuscript.Rmd
changed structure of the repository

```{r import, echo=FALSE, message=FALSE, warning=FALSE}
  # Please set your working directory using the drop down menu above
  # Then put this file in this directory, as well as the data.Rda file

  here::i_am("Manuscript.Rmd")

@@

  load(here("data.Rda"))

  # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
  consistencies <- read_rds(here("consistencies.rds"))
  # create a vector of consistencies to be used as the diagonal in a table later
  consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
                        format(round(t(consistencies[5,2:11]), digits = 2), nsmall = 2), rep(")",10))
  # paste together to create the output "alpha(omega)"
  consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")

>>>>

```{r import, echo=FALSE, message=FALSE, warning=FALSE}
  # Define the top level as the one where this file lies
  # If the rest of the files follow the structure of the Github project, everything will work

  here::i_am("flag_top_level_NFCBurnout.txt")

@@

  load(here("Data", "data.Rda"))

  # Load the internal consistencies (bootstrapping has been suppressed to save time on knitting)
  consistencies <- read_rds(here("Data", "consistencies.rds"))
  # create a vector of consistencies to be used as the diagonal in a table later
  consist_diag <- cbind(format(round(t(consistencies[2,2:11]), digits = 2), nsmall = 2), rep("(",10),
                        format(round(t(consistencies[5,2:11]), digits = 2), nsmall = 2), rep(")",10))
  # paste together to create the output "alpha(omega)"
  consist_diag <- apply(consist_diag[,c(1:4)], 1 ,paste, collapse = "")
